method

### 2021-12-06 06_Paper/ER-ED/method.Rmd
added figure arousal view
added graphics

#ggplot2::ggplot

@@

arousal_Reg = data_ER %>%
  subset(data_ER$block != "view_neu" & data_ER$block != "choice")

aov_arousalReg = afex::aov_ez(id = "ID",
                              dv = "arousal",
                              data = arousal_Reg,
                              within = "block",
                              fun_aggregate = mean)
afex::nice(aov_arousalReg, es = "pes")

@@

>>>>

# figure
ggplot2::ggplot(arousal_view, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neu", "view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

@@

arousal_reg = data_ER %>%
  subset(data_ER$block != "view_neu" & data_ER$block != "choice")

aov_arousalReg = afex::aov_ez(id = "ID",
                              dv = "arousal",
                              data = arousal_reg,
                              within = "block",
                              fun_aggregate = mean)
afex::nice(aov_arousalReg, es = "pes")

@@

# figure
ggplot2::ggplot(arousal_reg, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")
